### 2023-10-26 chapters/introduction.tex
Add photo credit to Kushim

\begin{figure}[t]
    \centering
    % \includegraphics[width=0.90\textwidth]{plimpton_322.png}
    \includegraphics[height=0.55\textheight]{kushim_multiplication.png}
    \caption[Technology is difficult. The accountant Kushim made mistakenly claimed $5 \times \sfrac{1}{2} = 5$.]{ Technology is difficult. Between 3400 and 3000 BCE, the Sumerian accountant Kushim wrote this tablet. Besides calculations of basic ingredients required for the production of cereal products, in the top left $6 \times 2$ grid it contains a multiplication table. While presumably aimed to ease the strenuous work of doing Sumerian mathematics, unfortunately, the top row states: $5 \times \sfrac{1}{2} = 5$, an unforgiving imprint the worlds first recorded mathematical error \parencite{nissen_archaic_1993, renn_learning_2019}, \parencite[photo credit][]{}.}
    \label{fig:kushim_multiplication}
\end{figure}
\todo[inline]{\cref{fig:kushim_multiplication} is awaiting response from CDLI with proper reference to tablet.}

>>>>

\begin{figure}[t]
    \centering
    % \includegraphics[width=0.90\textwidth]{plimpton_322.png}
    \includegraphics[height=0.55\textheight]{kushim_multiplication.png}
    \caption[Technology is difficult. The accountant Kushim made mistakenly claimed $5 \times \sfrac{1}{2} = 5$.]{ Technology is difficult. Between 3400 and 3000 BCE, the Sumerian accountant Kushim wrote this tablet. Besides calculations of basic ingredients required for the production of cereal products, in the top left $6 \times 2$ grid it contains a multiplication table. While presumably aimed to ease the strenuous work of doing Sumerian mathematics, unfortunately, the top row states: $5 \times \sfrac{1}{2} = 5$, an unforgiving imprint the worlds first recorded mathematical error \parencite{nissen_archaic_1993, renn_learning_2019}, \parencite[photo credit][]{cuneiformdigitallibraryinitiativecdli_msvo_2018}.}
    \label{fig:kushim_multiplication}
\end{figure}
\todo[inline]{\cref{fig:kushim_multiplication} is awaiting response from CDLI with proper reference to tablet.}
